Validation of Visual Statistical Inference, Applied to Linear Models

### 2012-06-21 paper_jasa.tex
difference between data plot p-value and min(null plot p-values)
comments on figure 7

An example lineup for slope $\beta=0.4$ is shown in Figure \ref{fig:test_contaminated}.  Can you pick which plot is different? %Plot 7 is the actual data plot. 
\begin{figure}[hbt]
%\begin{figurehere}
   \centering
       \scalebox{0.4}{\includegraphics{contaminated_data.pdf}}
       \caption{Scatterplot of a simulated contaminated data set generated such that a simple linear model produce a slope almost negligible, ie, if we fit model (Equation \ref{multi}) with $p=1$  to this data, the resulting estimate of $\beta_1$ would not be statistically significant.
}
       \label{fig:cont_dat}
\end{figure}

@@

\begin{figure}[hbtp]
   \centering
       \scalebox{0.70}{\includegraphics{power_loess_effect.pdf}}
       \caption{Observed power shown by loess smoother with simultaneous bootstrap confidence band and the power of conventional test. Responses are 1 and 0 depending on the success or failure respectively to identify the actual plot in the lineup. Size of the dots represents the number of responses for each lineup.}
       \label{fig:power_loess_effect}
\end{figure}

>>>>

An example lineup for slope $\beta=0.4$ is shown in Figure \ref{fig:test_contaminated}.  Can you pick which plot is different? %Plot 7 is the actual data plot. 
\begin{figure}[hbt]
%\begin{figurehere}
   \centering
       \scalebox{0.6}{\includegraphics{contaminated_data.pdf}}
       \caption{Scatterplot of a simulated contaminated data set generated such that a simple linear model produce a slope almost negligible, ie, if we fit model (Equation \ref{multi}) with $p=1$  to this data, the resulting estimate of $\beta_1$ would not be statistically significant. The conventional t-test $p$-value for the slope is 0.67 for this data set but visually we can see a convincing evidence of positive slope. 
}
       \label{fig:cont_dat}
\end{figure}

@@

\begin{figure}[hbtp]
   \centering
       \scalebox{0.70}{\includegraphics{power_loess_effect.pdf}}
       \caption{Observed power shown by loess smoother with simultaneous bootstrap confidence band and the power of conventional test. Responses are 1 and 0 depending on the success or failure respectively to identify the actual plot in the lineup. Size of the dots represents the number of responses for each lineup. \blue{Response to the intuition of Di: We are overestimating the effect for experiment 3 here because to compute effect I used the beta values of the linear part of the contaminated data. True effect should be much smaller since overall contaminated data should have a smaller slope. Thus the effect of 5 that the plot is showing now would actually be effect 2 (may be). That means the  power that we see in the plot for effect 5 is actually the power for effect 2. How can we get true effect for this data?
}}
       \label{fig:power_loess_effect}
\end{figure}
